An Experimental Evaluation of Hybrid Querying on Vectors (EA\&B)

### 2025-07-31 VLDB2026/main.tex
update fig

	\begin{minipage}[t]{0.38\textwidth}
		\centering
		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_multimodel.pdf}
		\hfill 
		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_multimodel_1.pdf}
		\caption{Multi-Modal Datasets}
		\label{fig:attribute-multimodal} 
	\end{minipage}%
	\hfill % 在盒子之间添加弹性间距
	%
	\begin{minipage}[t]{0.39\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_85.pdf}
		\hfill
		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_71.pdf}
		\caption{Different Platforms}
		\label{fig:attribute-cross-platform}
	\end{minipage}%
	\hfill
	%
	\begin{minipage}[t]{0.203\textwidth}
		\centering
		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf} 
		\caption{Large-Scale Dataset}
		\label{fig:attribute big dataset}
	\end{minipage}
\end{figure*}

@@

	\includegraphics[width=0.7\textwidth]{figures/exp/range_legend.pdf}

	\begin{minipage}[t]{0.38\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/range_multimodel.pdf}
		\hfill 
		\includegraphics[width=0.47\linewidth]{figures/exp/range_multimodel_1.pdf}
		\caption{Multi-Modal Datasets}
		\label{fig:range-multimodal} 
	\end{minipage}%
	\hfill % 在盒子之间添加弹性间距
	%
	\begin{minipage}[t]{0.39\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/range_85.pdf}
		\hfill
		\includegraphics[width=0.47\linewidth]{figures/exp/range_71.pdf}
		\caption{Different Platforms}
		\label{fig:range-cross-platform}
	\end{minipage}%
	\hfill
	%
	\begin{minipage}[t]{0.203\textwidth}
		\centering
		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf} 
		\caption{Large-Scale Dataset}
		\label{fig: range big dataset}
	\end{minipage}
\end{figure*}

@@

%	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Range}}
	\section{DISCUSSION}
	\textcolor{orange}{Based on the performance of algorithms across various experimental settings, we evaluate their strengths and weaknesses in different application scenarios, as shown in Table \ref{tab:algorithm_recommendation}. Next, we provide a detailed discussion of the advantages and disadvantages of each algorithm.}

@@

\begin{table*}[htbp]
	\caption{Algorithm Recommendation}
	\label{tab:algorithm_recommendation}
	\resizebox{\textwidth}{!}{

\begin{tabular}{|l|*{16}{c|}}
	\hline
	\multirow{2}{*}{\textbf{Application Scenarios / Algorithms}} 
	& \multicolumn{6}{c|}{\textbf{AF}} 
	& \multicolumn{5}{c|}{\textbf{RF}} 
	& \multicolumn{5}{c|}{\textbf{AF / RF}} \\
	\cline{2-17}
	& \textbf{UNG} & \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS} & \textbf{Puck} 
	& \textbf{Win} & \textbf{iRange} & \textbf{SeRF} & \textbf{DSG} & \textbf{UNIFY} 
	& \textbf{ACORN} & \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
	\hline
	\textbf{Performance Critical} & \textbf{B} & G & M & G & M & G & G & M & P & M & M & M/M & M/M & M/M & P/P & P/P \\
	\textbf{Fast Index Construction} & M & M & M & M & M & G & P & M & G & P & P & P/P & \textbf{B}/\textbf{B} & G/G & P/M & P/P \\
	\textbf{Memory Constraint} & M & P & M & M & M & G & P & P & M & P & P & P/P & \textbf{B}/\textbf{B} & G/M & G/M & G/G \\
	\textbf{Large-Scale Dataset} & \textbf{B} & G & G & P & P & G & \textbf{B} & G & M & M & G & M/P & P/M & P/P & M/M & - \\
	\textbf{Multi-Modal Dataset} & \textbf{B} & G & G & P & G & M & \textbf{B} & G & M & M & G & M/M & P/M & P/P & P/P & P/P \\
	\textbf{High LID Dataset} & \textbf{B} & G & M & G & M & M & \textbf{B} & G & M & M & G & P/P & M/G & P/P & P/M & P/P \\
	\textbf{Rare Attribute \& Low Range} & \textbf{B} & P & M & G & G & G & \textbf{B} & G & P & G & M & M/M & M/M & P/P & P/P & P/P \\
	\textbf{Robust to Attribute Distribution} & G & P & P & G & G & G & - & - & - & - & - & G/- & P/- & \textbf{B}/- & P/- & P/- \\
	\textbf{General-Purpose} & G & G & G & P & P & P & G & P & P & P & G & P & G & G & G & P \\
	\hline
\end{tabular}

	}
	\vspace{1mm}
\begin{flushleft}
	\textbf{Performance Levels:} \quad B = Best, G = Good , M = Moderate, P = Poor, - = Not Supported \\
\end{flushleft}
	\centering

>>>>

	\begin{minipage}[t]{0.38\textwidth}
		\centering
		% 内部图片宽度使用\linewidth，它会自适应为容器宽度(0.32\textwidth)
		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_multimodel.pdf}
		\hfill 
		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_multimodel_1.pdf}

	\end{minipage}%
	\hfill % 在盒子之间添加弹性间距
	%
	\begin{minipage}[t]{0.39\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/attribute_85.pdf}
		\hfill
		\includegraphics[width=0.47\linewidth]{figures/exp/attribute_71.pdf}

	\end{minipage}%
	\hfill
	%
	\begin{minipage}[t]{0.203\textwidth}
		\centering
		\includegraphics[width=0.96\linewidth]{figures/exp/attribute_100M.pdf}

	\end{minipage}
\end{figure*}

\begin{figure*}
	\centering
	\setlength{\abovecaptionskip}{0.0cm}
	\begin{minipage}[t]{0.37\textwidth}
		\centering
		\caption{Multi-Modal Datasets}
		\label{fig:attribute-multimodal}  
	\end{minipage}%
	\hfill % 在盒子之间添加弹性间距
	%
	\begin{minipage}[t]{0.37\textwidth}
		\centering
		\caption{Different Platforms}
		\label{fig:attribute-cross-platform}
	\end{minipage}%
	\hfill
	%
	\begin{minipage}[t]{0.24\textwidth}
		\centering
		\caption{Large-Scale Dataset}
		\label{fig:attribute big dataset}
	\end{minipage}
\end{figure*}

@@

\begin{figure*}
	\centering
	\includegraphics[width=0.7\textwidth]{figures/exp/range_legend.pdf}

	\begin{minipage}[t]{0.38\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/range_multimodel.pdf}
		\hfill 
		\includegraphics[width=0.47\linewidth]{figures/exp/range_multimodel_1.pdf}

	\end{minipage}%
	\hfill % 在盒子之间添加弹性间距
	%
	\begin{minipage}[t]{0.39\textwidth}
		\centering
		\includegraphics[width=0.495\linewidth]{figures/exp/range_85.pdf}
		\hfill
		\includegraphics[width=0.47\linewidth]{figures/exp/range_71.pdf}

	\end{minipage}%
	\hfill
	%
	\begin{minipage}[t]{0.203\textwidth}
		\centering
		\includegraphics[width=0.96\linewidth]{figures/exp/range_deep100M.pdf}

	\end{minipage}

\end{figure*}

\begin{figure*}
	\centering
	\setlength{\abovecaptionskip}{0.0cm}
	\begin{minipage}[t]{0.37\textwidth}
		\centering
		\caption{Multi-Modal Datasets}
		\label{fig:range-multimodal} 
	\end{minipage}%
	\hfill % 在盒子之间添加弹性间距
	%
	\begin{minipage}[t]{0.37\textwidth}
		\centering
		\caption{Different Platforms}
		\label{fig:range-cross-platform}
	\end{minipage}%
	\hfill
	%
	\begin{minipage}[t]{0.24\textwidth}
		\centering
		\caption{Large-Scale Dataset}
		\label{fig: range big dataset}
	\end{minipage}
\end{figure*}

@@

%	\textit{\textbf{Multimodel, 85 and Deep100M.}} \textcolor{red}{The fig is Figure \ref{fig:TrinityExtension——Range}}
	\section{DISCUSSION}
	Based on the performance of the algorithms on different experimental scenarios, we discuss our findings as follows.

@@

\begin{table*}[htbp]
	\caption{Algorithm Recommendation}
	\resizebox{\textwidth}{!}{
\begin{tabular}{|l|*{16}{c|}}
	\hline
	\multirow{2}{*}{\textbf{Application Scenarios / Algorithms}} 
	& \multicolumn{6}{c|}{\textbf{AF}} 
	& \multicolumn{5}{c|}{\textbf{RF}} 
	& \multicolumn{5}{c|}{\textbf{AF / RF}} \\
	\cline{2-17}
	& \textbf{NHQ} & \textbf{Filtered} & \textbf{Stitched} & \textbf{CAPS}  & \textbf{UNG} & \textbf{Puck} 
	& \textbf{DSG} & \textbf{iRange} & \textbf{SeRF} & \textbf{UNIFY} & \textbf{Win} 
	& \textbf{ACORN}& \textbf{Faiss} & \textbf{Milvus} & \textbf{VBASE} & \textbf{PASE} \\
	\hline
	\textbf{Query Performance} & S & M & S & M &\textbf{S} & S & M & M & W & M & S & M/M & M/M & M/M & W/W & W/W \\
	\textbf{Index Time} &M  &M  &M  &M  &M  &S  &W  &M  &S  &W  &W  &W/W &\textbf{S}/\textbf{S} &S/S  &W/M  &W/W  \\
	\textbf{Peak Memory} &W  &M  &M  &M  &M  &S  &W  &W  &M  &W  &W  &W/W  &\textbf{S}/\textbf{S}  &S/M  &S/M  &S/S \\
	\textbf{Large-Scale Dataset} & S & S & W & W &\textbf{S} &S  &M  &S  &M  &S  &\textbf{S}  &M/W  &W/M  &W/W  &M/M  &-  \\
	\textbf{Rare Attribute \& Low Range} &M  &M  &S  &S &\textbf{S}  &S  &S  &S  &W  &M  &\textbf{S} &M/M  &M/M  &W/W  &W/W  &W/W  \\
	\textbf{Robust to Multi-Modal Dataset} &S  &S  &W  &S  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &M/M  &W/M  &W/W  &W/W  &W/W  \\
	\textbf{Robust to Attribute Distribution} &W  &W  &S  &S  &S  &S  &-  &-  &-  &-  &-  &S/-  &W/-  &\textbf{S}/-  &W/-  &W/-  \\
	\textbf{High LID Dataset} &S  &M  &S  &M  &\textbf{S}  &M  &M  &S  &M  &S  &\textbf{S}  &W/W  &M/S  &W/W  &W/M  &W/W  \\
	\textbf{General-Purpose} &\faCheck  &\faCheck  &\faTimes  &\faTimes  &\faCheck  &\faTimes  &\faTimes  &\faTimes &\faTimes  & \faCheck &\faCheck&\faTimes  &\faCheck  &\faCheck  &\faCheck&\faTimes  \\
	\hline
\end{tabular}
	}
	\vspace{1mm}
\begin{flushleft}
	\textbf{Performance Levels:} \quad \textbf{S} = Strongest, S = Strong, M = Medium, W = Weak, - = Not Supported \\
	\textbf{Recommendation:} \quad \faCheck = Recommended, \faTimes = Not Recommended
\end{flushleft}
	\centering
